\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {July 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {placeholder}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern (Part Time)} % Job title
    {Toast} % Organization
    {Boston, MA} % Location
    {Feb. 2019 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {placeholder}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Drizly} % Organization
    {Boston, MA} % Location
    {May. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a re-designed onboarding flow for new retailer customers, improving the onboarding process for account managers and customers with automated Salesforce integration.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {Jan. 2018 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped migrate the Instagram Django web server to perform parallel IO operations and handle concurrent requests within each worker process to reduce latency and increase capacity as the web framework scales with users, servers, and developers.}
		\item {Created a framework to safely predict the performance and correctness of server worker processes handling concurrent requests from a production environment. Preemptively caught and fixed regressions related to increased cpu instructions, caching, and global state contamination}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Toast} % Organization
    {Boston, MA} % Location
    {Jan. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a microservice, database schema, and related web pages to manage customer accounts --- 50,000+ created within the first two months.}
		\item {Designed and helped implement a second microservice as a month-long architecture refactor to reduce technical debt and build the infrastructure for upcoming payment features.}
		\item {Enhanced the audit tool to query real-time data from restaurants' Android devices, proactively resolving customers' configuration bugs.}
      \end{cvitems}
    }

  \cventry
    {Programming Mentor, TA} % Job title
    {CSTUY Hacking Sessions} % Organization
    {New York, NY} % Location
    {Sept. 2014 - Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught programming concepts to high school students using Java and Processing while providing input for lesson plans and project ideas.}
      \end{cvitems}
    }    
\end{cventries}
